### 2017-10-13 Gruba/02-overview.tex

\begin{definition}
\label{def:blog}
A microblog $M_b = (O, T, M, flag)$ consists of the owner $O$ (a.k.a. user in this paper) to whom $M_b$ belongs (either created or \retd{}), the timestamp $T$ showing when $M_b$ is generated, the microblog message $M$ and a bit $flag$ denoting $M_b$ is \retd{} (1) or originally created (0) by the owner $O$.
\end{definition}

@@

\begin{definition}
\label{def:user}
A user $u = (B_u, R_u, E_u)$ consists of three sets regarding the user's microblogs $B_u$, followers $R_u$ and followees $E_u$ separately.
Each follower/followee per se refers to a user.
\end{definition}

@@

\subsection{\sys{} Framework}
\sys{} is designed from the ground up as a system for modeling users' \retg{} behavior in social media.
Figure \ref{fig:framework} shows the architectural components of \sys{}, mainly comprising Sina Microblog Data, Key Modules and Profile Demonstrator.

\begin{figure}[tb!]
\centering
\includegraphics[width=.7\linewidth]{figures/architecture.pdf}
\caption{\sys{} Architecture}
\label{fig:framework}
\end{figure}

@@

	\stab(1)  Feature Extraction: By coalescing the microblog data, each user is depicted by a bunch of features, which are grouped into three categories. They are features of \textit{Basics} (e.g., the number of followers and followees), \textit{Behavior} (e.g., the frequency and the popular slots of \retg{}) and \textit{Interest} (e.g., the long-term/recent interests, as well as the explicit/implicit interests). These features are extracted from the stored data by Feature Extraction module and serve as the input of User Clustering module.

@@

	\stab(3)  Behavior Modeling: For each group obtained by User Clustering, Behavior Modeling employs both positive and negative samples (i.e., microblogs that were labeled with \retd{} and not \retd{}) to train a model, over which the testing of users' \retg{} behavior is performed.
%\end{enumerate}

@@

>>>>

\begin{definition}
\label{def:blog}
A microblog $M_b = (O, T, M, flag)$ has its owner $O$ (a.k.a. user in this paper) to whom $M_b$ belongs (either created or \retd{}), the generated time $T$ of $M_b$, the message context $M$, and $flag$ denoting $M_b$ is \retd{} (1) or originally created (0) by $O$.
\end{definition}

@@

\begin{definition}
\label{def:user}
A user $u = (B_u, R_u, E_u)$ consists of three sets regarding the user's microblogs $B_u$, followers $R_u$ and followees $E_u$, in which each follower/followee per se refers to a user.
\end{definition}

@@

\subsection{\sys{} Framework}
\sys{} is designed from the ground up as a system for modeling users' \retg{} behavior in social media.
Figure \ref{fig:framework} shows the architectural components of \sys{}. %, mainly comprising Sina Microblog Data, Key Modules and Profile Demonstrator.

\begin{figure}[tb!]
\centering
\includegraphics[width=.67\linewidth]{figures/architecture.pdf}
\vspace{-1ex}
\caption{\sys{} Architecture}
\label{fig:framework}
\vspace{-4ex}
\end{figure}

@@

	\stab(1)  Feature Extraction: By coalescing the microblog data, each user is depicted by a bunch of features, which are grouped into three categories. They are features of \textit{Basics} (e.g., the number of followers and followees), \textit{Behavior} (e.g., the frequency and the popular slots of \retg{}) and \textit{Interest} (e.g., the long-term/recent interests, as well as the explicit/implicit interests). These features are extracted from the stored  Sina Weibo data by Feature Extraction module, and serve as the input of the User Clustering module.

@@

	\stab(3)  Behavior Modeling: For each group obtained by User Clustering, Behavior Modeling builds a  model by employing both positive and negative samples (i.e., microblogs that are labeled with \retd{} and not \retd{}), over which the testing of users' \retg{} behavior is performed.
%\end{enumerate}

@@

System  \sys{} models user behaviors over groups instead of the mono model for all users.

\begin{table}[tb!]
\centering
\begin{small}
\caption{Illustration of Variables in Basic Feature}
\vspace{0.3cm}
\label{tbl:fe-info}
\begin{tabular}{ll}
\toprule
\multicolumn{1}{l}{\textbf{Variables}} & \multicolumn{1}{l}{\textbf{Illustration}}	\\	\midrule \midrule
\#$R_u$				& number of followers				\\	\midrule
\#$E_u$				& number of followees				\\	\midrule
                    & a ratio defined as the number of followers over \\
\raisebox{1.5ex}{$R_{ee}$}  & that of followees, i.e., ${\#R_u}/{\#E_u}$ \\  \midrule
$U_t$					& user type (as detailed in Table \ref{tbl:ucate})			\\ \bottomrule
\end{tabular}
\end{small}
\vspace{-3ex}
\end{table}
\begin{table}[tb!]
\centering
\begin{small}
\caption{Category of User Type}
\vspace{0.3cm}
\label{tbl:ucate}
\begin{tabular}{ll}
\toprule
\multicolumn{1}{l}{\textbf{Values}} & \multicolumn{1}{l}{\textbf{Illustration}}	\\	\midrule \midrule
0                       & $\#E_u \le 50 \ {\bf and} \ \#R_u \le 50$				\\	\midrule
\multirow{2}{*}{1}      & \multirow{2}{*}{$\frac{\#E_u}{\#R_u} \ \ge 5$}	\\
 						&                       									\\	\midrule
\multirow{2}{*}{2}		& \multirow{2}{*}{$\frac{\#R_u}{\#E_u} \ \ge 5$}  \\
						&															\\	\midrule
3                   	& other cases 												\\ \bottomrule
\end{tabular}
\end{small}
\end{table}
